---
title: "Develoing Data Products - Interactive Map"
author: "Sohini Mukherjee"
date: "15/02/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Submission

Here is an interactive map of historical locations of my hometown Kolkata (Calcutta).

The following locations are included-

-1. Victoria Memorial


-2. Fort William


-3. Howrah Bridge


-4. Writer's Building


-5. Jorasankho Thakurbari Rabindranath Tagore's House 


-6. Eden Gardens Stadium




```{r cars, include=FALSE}
library(knitr)
library(leaflet)
library(dplyr)
```


## Historical Places on the map of Kolkata
```{r}
m <- leaflet() %>%
  addTiles() %>% 
  addMarkers(lat=22.5448, lng=88.3426, popup="Victoria Memorial") %>%
  addMarkers(lat=22.5542,lng=88.3359, popup="Fort William") %>%
  addMarkers(lat=22.5851,lng=88.3468, popup="Howrah Bridge") %>%
  addMarkers(lat=22.5738,lng=88.3487, popup="Writer's Building") %>%
  addMarkers(lat=22.5855,lng=88.3568, popup="Jorasankho Thakurbari") %>%
  addMarkers(lat=22.5646,lng=88.3433, popup="Eden Gardens Stadium") #%>%
#setView (lat=22.5726, lng=88.3639, zoom=16)
m # Print the map
```

## Mapping Clusters
When you zoom in to each cluster, the cluster will seperate until you see the individual Markers!

```{r}
df <- data.frame(lat=runif(500, min=22.47, max = 22.57 ), lng=runif(500, min=88.36, max = 88.46)) 
df %>%
leaflet() %>%
addTiles() %>%  
addMarkers(clusterOptions = markerClusterOptions())
```
